Generalization Errors of Hard Parameter Sharing: High-dimensional Asymptotics and Implications

### 2020-09-13 arxiv/setup.tex
wip

%\section{Preliminaries}

\paragraph{Notations.}
We shall say an event $\Xi$ holds with high probability (w.h.p.) if for any fixed $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$. Moreover, we shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p\to \infty$.
For a matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.
We shall refer to random matrices of the form $\frac {X^\top X} n$ as sample covariance matrices following the standard notations in high-dimensional statistics.
%\subsection{Bias and Variance}

@@

%\subsection{Hard Parameter Sharing}

%\subsection{Random Matrices}
\todo{merge w/ theorem}
We make several standard assumptions on the covariance matrix $\Sigma_k$ and the random vector $z_i$, for $k = 1,\dots, t$ and $i = 1,\dots, n_k$.
First, for every entry of $z_i$, we assume that its $(4+\e)$-th moment exists, that is, there exist constants $\e, C > 0$ such that
\begin{equation}\label{assmAhigh}
	\ex{\abs{z_{i,j}}^{4+\e}} \le C,\ 1\le j \le p.
\end{equation}
Second, we assume that the spectral norm of $\Sigma_k$ is bounded by a fixed constant, for every $k = 1,\dots, t$.
This is without loss of generality since we can always rescale $\Sigma_k$ so that its spectral norm satisfies the condition.
Finally, for the noise vector $\varepsilon_k$, we assume that there exists an absolute constant such that for all $l$ \todo{check, remove $c$ and $o(1)$ in main body}, the $l$-th moment of the noise entries exists:
\begin{align*}
	\ex{\abs{\varepsilon_{k, j}}^l \le C}, \text{ for all } j = 1, \dots, n_k.
\end{align*}

>>>>

\section{Preliminaries}

\subsection{Notations.}
We shall say an event $\Xi$ holds with high probability (w.h.p.) if for any fixed $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$. Moreover, we shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p\to \infty$.
For a matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.
We shall refer to random matrices of the form $\frac {X^\top X} n$ as sample covariance matrices following the standard notations in high-dimensional statistics.
%\subsection{Bias and Variance}

Let $A = [a_1, a_2, \dots, a_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.

@@

\subsection{Hard Parameter Sharing}

\subsection{Random Matrices}
\todo{merge w/ theorem}
We make several standard assumptions on the covariance matrix $\Sigma_k$ and the random vector $z_i$, for $k = 1,\dots, t$ and $i = 1,\dots, n_k$.
First, for every entry of $z_i$, we assume that its $(4+\e)$-th moment exists, that is, there exist constants $\e, C > 0$ such that
\begin{equation}\label{assmAhigh}
	\ex{\abs{z_{i,j}}^{4+\e}} \le C,\ 1\le j \le p.
\end{equation}
Second, we assume that the spectral norm of $\Sigma_k$ is bounded by a fixed constant, for every $k = 1,\dots, t$.
This is without loss of generality since we can always rescale $\Sigma_k$ so that its spectral norm satisfies the condition.
Finally, for the noise vector $\varepsilon_k$, we assume that there exists an absolute constant such that for all $l$ \todo{check, remove $c$ and $o(1)$ in main body}, the $l$-th moment of the noise entries exists:
\begin{align*}
	\ex{\abs{\varepsilon_{k, j}}^l \le C}, \text{ for all } j = 1, \dots, n_k.
\end{align*}
